OECD TiVa LMIC GVCs

### 2015-04-21 OECD-TiVa-LMIC-GVCs.Rmd
add LaTeX
add CEQ for china plot to pres

@@

# merge gvc indicators and nrca
gvc_indicators %<>% merge(nrca, by.x = c("ctry", "isic", "year"), by.y = c("country", "industry", "year") )
```

@@

>>>>

$$E_x$$

@@

# merge gvc indicators and nrca
gvc_indicators %<>% merge(nrca, by.x = c("ctry", "isic", "year"), by.y = c("country", "industry", "year") )
gvc_indicators %<>% merge(trca, by = c("ctry", "isic", "year") )
```

@@

## CEQ of China

```{r, echo=FALSE} 
# TRCA vs NRCA for China, ELQ
gvc_indicators %>%
  filter(ctry == "chn") %>%
  filter(ind_name == "elq") %>%
  group_by(year) %>%
  summarise( trca = sum(rca), nrca = sum(nrca) ) %>%
  ggvis(~year, ~trca, stroke = "trca") %>%
  layer_lines() %>%
  layer_lines(~year, ~nrca, stroke="nrca")
```
